Imposing a Weight Norm Constraint for Neuro-Adaptive Control

### 2025-06-19 presentation/presentation.tex
adding notes

% https://www.overleaf.com/learn/latex/Beamer#Using_a_colorthemev

% Inbuilt themes in beamer
% \documentclass[8pt, aspectratio=169, handout]{beamer}
\documentclass[8pt, aspectratio=169]{beamer}
% \setbeamertemplate{caption}[numbered]

\input{../template/macros/macros_general.tex}
\input{../template/macros/macros_math.tex}
\input{../template/symbols/symbols_NN.tex}
\input{../template/symbols/symbols_robot.tex}

% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% Block options: block, alertblock, exampleblock
% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

% % Theme choice:
% \usetheme{Antibes}
% % \usecolortheme{beaver}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% Use roboto Font (recommended)
% \usepackage[sfdefault]{roboto}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% Define where theme files are located. ('/styles')
\usepackage{styles/fluxmacros}
\usefolder{styles}
% Use Flux theme v0.1 beta
% Available style: asphalt, blue, red, green, gray 
\usetheme[style=dding]{flux}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% Extra packages for the demo:
\usepackage{booktabs}
\usepackage{colortbl}
\usepackage{ragged2e}
\usepackage{schemabloc}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

\usepackage{multirow}
\usepackage{media9}

% https://latexcolor.com % color list
\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
\definecolor{awesome}{rgb}{1.0, 0.13, 0.32}
\newcommand{\ctxt}[2]{\color{#1}{#2}\color{black} }
% \newcommand{\ctxt}[2]{\color{#1}\mathbf{#2}\color{black} }

% Title page details: 
\title{
    Imposing a Weight Norm Constraint for Neuro-Adaptive Control 
} 
\subtitle{
    \textit{IEEE European Control Conference (ECC) 2025}\\
}
\author{
  \textbf{\ctxt{airforceblue}{Myeongseok Ryu}}\inst{1}, Jiyun Kim\inst{2}, and Kyunghwan Choi\inst{1}
  }
\date{2025-06-25}
\institute{%
    \begin{minipage}[c]{\linewidth}
        \centering
        \inst{1}%
        Mobility Intelligence and Control Laboratory (MIC Lab) \\
        % Department of Mechanical and Robotics Engineering\\
        % Gwangju Institute of Science and Technology
        CCS Graduate School of Mobility \\
        Korea Advanced Institute of Science and Technology (KAIST)
        \and
        \inst{2}%
        AI Graduate School\\
        Gwangju Institute of Science and Technology (GIST)
  \end{minipage}
}

@@

% \AtBeginSubsection[]{%
%   \begin{frame}
%   \vfill
%   \centering
%     \insertsectionhead
%     \\
%     \large\textbf{\insertsubsectionhead}
%   \vfill
%   \end{frame}
% }

@@

% Title page frame
\titlepage

% Outline frame
\begin{frame}{Outline}
    \tableofcontents
\end{frame}

@@

\begin{frame}{\insertsubsectionhead}{What is Neuro-Adaptive Control?}

@@

\begin{frame}{\insertsubsectionhead}{What is Neuro-Adaptive Control?}

@@

\begin{frame}{\insertsubsectionhead}{What is Neuro-Adaptive Control?}

@@

\subsection{Literature Review}

\begin{frame}{\insertsubsectionhead}

@@

  \vspace{0.5cm}

@@

\begin{frame}{\insertsubsectionhead}{Limitations of Existing Methods}

@@

\subsection{Contributions}

\begin{frame}{\insertsubsectionhead}

@@

% ╔═══════════════════════════════════════════════╗
% ║ Section: Proposed Method                      ║
% ╚═══════════════════════════════════════════════╝
\section{Proposed Method}

@@

\begin{frame}{\insertsubsectionhead}

@@

@@

@@

\begin{frame}{\insertsubsectionhead}{Gradient Descent/Ascent Method}

@@

    \end{block}
  \end{minipage}
\end{frame}

@@

\begin{frame}{\insertsubsectionhead}{Lyapunov Stability Analysis}

@@

\begin{frame}{\insertsubsectionhead}{Two-Link Robotic Manipulator}

@@

\begin{frame}{\insertsubsectionhead}{Controllers Setting}

@@

\begin{frame}{\insertsubsectionhead}{Controllers for Comparative Study}

@@

\begin{frame}{\insertsubsectionhead}{Box-and-Whisker Plots}

@@

\begin{frame}{\insertsubsectionhead}{Weight Norms}

@@

\begin{frame}{\insertsubsectionhead}{Tracking Performance}

@@

\begin{frame}{Real-time Implementation Result}

@@

\begin{frame}{Conclusion}

@@

\section{}
\begin{frame}{}
    \centering \Large
    \emph{Thank you for your attention!}
\end{frame}

\begin{frame}[allowframebreaks]{References}

>>>>

\documentclass[8pt, aspectratio=169, handout]{beamer}
% \documentclass[8pt, aspectratio=169]{beamer}

% For figure numbering
% \setbeamertemplate{caption}[numbered]

% Slide show note
% \setbeameroption{hide notes}
% \setbeameroption{show only notes}
\setbeameroption{show notes on second screen}

% MIC Lab template
\input{../template/macros/macros_general.tex}
\input{../template/macros/macros_math.tex}
\input{../template/symbols/symbols_NN.tex}
\input{../template/symbols/symbols_robot.tex}

% Block options: block, alertblock, exampleblock

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% Use roboto Font (recommended)
% \usepackage[sfdefault]{roboto}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% Define where theme files are located. ('/styles')
\usepackage{styles/fluxmacros}
\usefolder{styles}
% Use Flux theme v0.1 beta
% Available style: asphalt, blue, red, green, gray, dding (custom)
\usetheme[style=dding]{flux}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% Extra packages for the demo:
\usepackage{booktabs}
\usepackage{colortbl}
\usepackage{ragged2e}
\usepackage{schemabloc}
\usepackage{multirow}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% for video
\usepackage{media9}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% colors
% https://latexcolor.com % color list
\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
\definecolor{awesome}{rgb}{1.0, 0.13, 0.32}
\newcommand{\ctxt}[2]{\color{#1}{#2}\color{black}}
% \newcommand{\mtxt}[2]{\color{#1}\mathbf{#2}\color{black} }
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% Title page details: 
\title{
    Imposing a Weight Norm Constraint for Neuro-Adaptive Control 
} 
\subtitle{
    \textit{IEEE European Control Conference (ECC) 2025}\\
}
\author{
  \textbf{\ctxt{airforceblue}{Myeongseok Ryu}}\inst{1}, Jiyun Kim\inst{2}, and Kyunghwan Choi\inst{1}
  }
\date{2025-06-25}
\institute{%
    \begin{minipage}[c]{\linewidth}
        \centering
        \inst{1}%
        Mobility Intelligence and Control Laboratory (MIC Lab) \\
        % Department of Mechanical and Robotics Engineering\\
        % Gwangju Institute of Science and Technology
        CCS Graduate School of Mobility \\
        Korea Advanced Institute of Science and Technology (KAIST)
        \and
        \inst{2}%
        AI Graduate School\\
        Gwangju Institute of Science and Technology (GIST)
  \end{minipage}
}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% Global settings

@@

% \AtBeginSubsection[]{%
%   \begin{frame}
%   \vfill
%   \centering
%     \insertsectionhead
%     \\
%     \large\textbf{\insertsubsectionhead}
%   \vfill
%   \end{frame}
% }
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

@@

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% Title page frame
\titlepage

% Outline frame
\begin{frame}{Outline}
  \tableofcontents
\end{frame}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

@@

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{frame}{\insertsubsectionhead}{What is Neuro-Adaptive Control?}

@@

\end{frame} 
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

\note[enumerate]
{
  \item adaptive controls adapts their parameters in real-time to systems.
  \begin{itemize}
    \item Hence, they can handle uncertainties and disturbances.
  \end{itemize}
  \item Like adaptive control, NAC adapts its NN weights, as well.
  \item Hence, it has both features of NN and adaptive control.
}

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{frame}{\insertsubsectionhead}{What is Neuro-Adaptive Control?}

@@

\end{frame}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

\note[enumerate]
{
  \item The features are...
  \begin{itemize}
    \item It can adapts its weights to change environments.
    \item And the stability is ensured in the sense of Lyapunov.
    \item So, it has online learning capability.
    \item In addition, with various methods from adaptive control, NAC can be more robust than naive NN-based control methods.
  \end{itemize}
}

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{frame}{\insertsubsectionhead}{What is Neuro-Adaptive Control?}

@@

\end{frame}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

\note[enumerate]
{
  \item However, there are some challenges in NAC.
  \item The first challenge is weight boundedness.
  \begin{itemize}
    \item If the NNs are used for control naively, the boundedness of NN weights is not ensured.
    \item Despite the convergence of the control error, the NN weights can diverge like parameter drift.
    \item This divergence leads to the following issue.
  \end{itemize}
  \item Second one is the NN's output can be excessively large control inputs.
  \begin{itemize}
    \item This is because, the output of NN is not interpretable and unpredictable.
    \item So, the input saturation problem can occur by them.
  \end{itemize}
}

% ╔═══════════════════════════════════════════════╗
% ║ Section: Background and Contributions         ║
% ║   - Subsection: Literature Review             ║
% ╚═══════════════════════════════════════════════╝
\subsection{Literature Review}

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{frame}{\insertsubsectionhead}

@@

  % \vspace{0.5cm}

@@

\end{frame}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

\note[enumerate]
{
  \item To address these issues, several methods have been introduced.
  \item For weight boundedness, the projection operator and modification methods are used.
  \begin{itemize}
    \item they ensures the weight boundedness by projects onto a convex set or adding a stabilizing term.
    \item Hence, the the boundedness of NN weights can 
  \end{itemize}
  \item For control input saturation, additional control inputs are used.
  \begin{itemize}
    \item Conventionally, auxiliary system-based control inputs or, more recently, barrier Lyapunov function-based control inputs are used.
    \item For this, the nominal model knowledge is required.
    \item These makes the control design more complicated, but, have shown the effectiveness of the control input saturation handling.
  \end{itemize}
}

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{frame}{\insertsubsectionhead}{Limitations of Existing Methods}

@@

\end{frame}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

\note[enumerate]
{
  \item the limitations of the existing methods can be summarized as follows.
  \item Most of methods does not consider the optimality when the constraints are active.
  \item 
}

% ╔═══════════════════════════════════════════════╗
% ║ Section: Background and Contributions         ║
% ║   - Subsection: Contributions                 ║
% ╚═══════════════════════════════════════════════╝
\subsection{Contributions}

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{frame}{\insertsubsectionhead}

@@

\end{frame}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

% ╔═══════════════════════════════════════════════╗
% ║ Section: Proposed Method                      ║
% ╚═══════════════════════════════════════════════╝

\section{Proposed Method}

@@

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{frame}{\insertsubsectionhead}

@@

\end{frame}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

@@

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{frame}{\insertsubsectionhead}{Optimization Problem}

@@

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{frame}{\insertsubsectionhead}{Gradient Descent/Ascent Method}

@@

    \end{block}
  \end{minipage}
\end{frame}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

@@

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{frame}{\insertsubsectionhead}{Lyapunov Stability Analysis}

@@

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{frame}{\insertsubsectionhead}{Two-Link Robotic Manipulator}

@@

\end{frame}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{frame}{\insertsubsectionhead}{Controllers Setting}

@@

\end{frame}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{frame}{\insertsubsectionhead}{Controllers for Comparative Study}

@@

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{frame}{\insertsubsectionhead}{Box-and-Whisker Plots}

@@

\end{frame}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{frame}{\insertsubsectionhead}{Weight Norms}

@@

\end{frame}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{frame}{\insertsubsectionhead}{Tracking Performance}

@@

\end{frame}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{frame}{Real-time Implementation Result}

@@

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{frame}{Conclusion}

@@

\end{frame}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\section{}
\begin{frame}{}
    \centering \Large
    \emph{Thank you for your attention!}
\end{frame}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{frame}[allowframebreaks]{References}
